---
title: "HW9"
author: "Angela Zhao"
output: pdf_document
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60))
```

```{r echo=FALSE,message=FALSE}
#load libraries
library(tidyverse)
library(mosaic)
library(MatchIt)
library(moderndive)
library(kableExtra)
#datasets
turnout <- read_csv('turnout.csv')
solder <- read_csv('solder.csv')
```

az9934  
https://github.com/angela2zhao/HW9


# **Problem 1**

# Part A
```{r echo = FALSE}
# proportion of those receiving and not receiving calls that voted in 1998
prop(voted1998~GOTV_call, data=turnout)

#95% confidence interval for the difference in these two proportions
boot_called = do(10000) * diffprop(voted1998~GOTV_call, data=mosaic::resample(turnout))
confint(boot_called, level=0.95)
```

# Part B
```{r echo = FALSE}
# proportion of people who voted in 1996 and whether they received a call
xtabs(~ voted1996 + GOTV_call, data=turnout) %>%
  prop.table(margin=2)

# average age for those receiving and not receiving calls
mean(AGE~GOTV_call,data=turnout)

# proportion of people who are registered as a member of a major party and whether they received a call 
#majorpty
xtabs(~ MAJORPTY + GOTV_call, data=turnout) %>%
  prop.table(margin=2)
```

# Part C
```{r echo = FALSE}
#matched data set
turnout_matched = matchit(GOTV_call ~ voted1996 + AGE + MAJORPTY, data=turnout, ratio=5) %>%
  match.data

#verify matched data set
xtabs(~ voted1996 + GOTV_call, data=turnout_matched) %>%
  prop.table(margin=2)
mean(AGE~GOTV_call,data=turnout_matched)
xtabs(~ MAJORPTY + GOTV_call, data=turnout_matched) %>%
  prop.table(margin=2)
```

\newpage
```{r echo = FALSE}
#recalculate part a with matched data
prop(voted1998~GOTV_call, data=turnout_matched)
boot_called = do(10000) * diffprop(voted1998~GOTV_call, data=mosaic::resample(turnout_matched))
confint(boot_called, level=0.95)
```

The overall effect of the GOTV call on the likelihood of voting in the 1998 election is present because the confidence interval is statistically significant, but it is fairly small. 


# **Problem 2**

# Part A
```{r echo = FALSE}
ggplot(solder) + geom_boxplot(aes(x=Opening,y=skips)) + labs(title="Relationship Between Opening Size and Skips",x="Opening Size")
```
The plot above shows how as the size of the opening on the solder gun gets smaller, the number of skips increases overall. 

```{r echo = FALSE}
ggplot(solder) + geom_boxplot(aes(x=Solder,y=skips)) + labs(title="Relationship Between Solder Thickness and Skips",x="Solder Thickness")
```
The plot above shows how using a thin alloy will result in more skips overall than using a thick alloy

# Part B
```{r echo=FALSE}
#regression model
solder_model = lm(skips ~ Opening + Solder + Opening:Solder, data=solder)

# regression table
solder_table = get_regression_table(solder_model,conf.level = 0.95, digits=2) %>%
  select(term, estimate, lower_ci,upper_ci)

#table
kable(solder_table,col.names = c("coefs","estimates","lower ci","upper ci"))
```

\newpage

# Part C
When the opening of the solder gun was medium sized, the number of solder skips on the circuit board was 2.41 skips higher.  
When the opening of the solder gun was small sized, the number of solder skips on the circuit board was 5.13 skips higher.  
When the opening of the solder gun was medium sized, the number of solder skips on the circuit board was 2.28 skips higher.  
When the opening of the solder gun was medium sized and the thickness of the alloy used for soldering was thin, the number of solder skips on the circuit board was 0.74 skips lower.    
When the opening of the solder gun was small sized and the thickness of the alloy used for soldering was thick, the number of solder skips on the circuit board was 9.65 skips higher.  

# Part D
I would recommend an small opening size and thin alloy for the soldering to AT&T based on this analysis. The coefficient for this interaction was negative, which means that it can decrease the number of skips. 